\documentclass[a4paper,12pt]{article}

\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{
    total={150mm,237mm},
    left=30mm,
    top=30mm,
}
\usepackage{amsmath}
\usepackage{multicol}

\setlength{\parindent}{0pt}

\begin{document}
\large
\section*{Simple Quadratic Equations}

\subsection*{Example Problems}

\textsc{Example 1}: Solve the following equation for $x$,
$$x^2 = 49.$$

\textsc{Solution}: To find the answer to the equation we need to
find the square root of both sides of the equation,
$$\sqrt{x^2} = \sqrt{49},$$
the LHS simplifies and for the RHS we can evaluate the square root,
$$x = \pm 7.$$
Note here that the $\pm$ is important since $7^2 = 49$ and 
$(-7)^2 = 49$ so we use it to indicate that $x = -7 \textrm{ or } 7$.

\vspace{3mm}
\hrule
\vspace{3mm}

\textsc{Example 2}: Solve the following equation for $x$,
$$3x^2 - 19 = 56.$$

\textsc{Solution}: In order to simplify the LHS, we first will 
remove the $-19$ since it is the last operation performed on $x$.
We can do this by adding 19 to both sides
\begin{align*}
3x^2 - 19 + 19 &= 56 + 19, \\
3x^2 &= 75.
\end{align*}
Next we will divide both sides by 3,
\begin{align*}
3x^2 \div 3 &= 75 \div 3, \\
x^2 &= 25,
\end{align*}
and finally square root both sides,
\begin{align*}
\sqrt{x^2} &= \sqrt{25}, \\
x &= \pm 5.
\end{align*}

\vspace{3mm}
\hrule
\vspace{3mm}

\textsc{Example 3}: Solve the following equation for $x$,
$$\frac{x^2 - 12}{4} = 13.$$

\textsc{Solution}: To simplify the LHS first we need to notice that
the numerator of the fraction has implicit brackets,
$$\frac{(x^2 - 12)}{4} = 13,$$
which means that we first need to multiply both sides by 4,
\begin{align*}
\frac{x^2 - 12}{4} \times 4 &= 13 \times 4, \\
x^2 - 12 &= 52,
\end{align*}
then we add 12 and square root
\begin{align*}
x^2 - 12 + 12 &= 52 + 12, \\
x^2 &= 64, \\
\sqrt{x^2} &= \sqrt{64}, \\
x &= \pm 8.
\end{align*}

\newpage
\subsection*{Question Bank}

\textsc{Note}: Any questions where you get a decimal as an answer
can be rounded to 2 decimal places.

\begin{enumerate}
\item Solve the following equations.
    \begin{multicols}{2}
    \begin{enumerate}
    \item $x^2 = 9$
    \item $x^2 = 1$
    \item $x^2 = 441$
    \item $x^2 = 169$
    \item $x^2 = 0$
    \item $x^2 = 200$
    \end{enumerate}
    \end{multicols}

\item Solve the following equations.
    \begin{multicols}{2}
    \begin{enumerate}
    \item $5x^2 = 45$
    \item $13x^2 = 637$
    \item $-3x^2 = -27$
    \item $x^2 + 14 = 95$
    \item $x^2 - 17 = 47$
    \item $x^2 - 256 = -87$
    \item $x^2 - 36 = 0$
    \item $\displaystyle\frac{x^2}{3} = 27$
    \item $\displaystyle\frac{x^2}{4} = 25$
    \item $\displaystyle\frac{x^2}{28} = \frac{9}{7}$
    \item $\displaystyle\frac{x^2}{52} = 3.25$
    \item $\displaystyle\frac{-x^2}{4} = -16$
    \end{enumerate}
    \end{multicols}

\item Solve the following equations for $x$.
    \begin{multicols}{2}
    \begin{enumerate}
    \item $5x^2 + 14 = 59$
    \item $3x^2 - 270 = 162$
    \item $7x^2 - 53 = -25$
    \item $2x^2 + 42 = 140$
    \item $\displaystyle \frac{x^2}{8}-13 = -11$
    \item $\displaystyle \frac{x^2}{6} + 25 = 49$
    \item $\displaystyle \frac{x^2}{12} + 15.25 = 22$
    \item $\displaystyle \frac{x^2}{64} + \frac{15}{4} = 6$
    \end{enumerate}
    \end{multicols}

\item Solve the following equations for $x$.
    \begin{multicols}{2}
    \begin{enumerate}
    \item $-x^2 = -25$
    \item $-3x^2 = -363$
    \item $\displaystyle \frac{-x^2}{5} = -20$
    \item $\displaystyle \frac{-3x^2}{4} = -27$
    \item $-x^2 + 9 = -40$
    \item $-x^2 - 17 = -33$
    \item $45 - x^2 = 9$
    \item $23 - x^2 = -58$
    \item $14 - 2x^2 = -36$
    \item $48 - 3x^2 = 11$
    \end{enumerate}
    \end{multicols}

\item Solve the following equations for $x$.
    \begin{multicols}{2}
    \begin{enumerate}
    \item $3(x^2 + 9) = 102$
    \item $8(x^2 - 36) = -160$
    \item $2(3x^2 - 10) = 4$
    \item $11(5x^2 + 21) = 1111$
    \item $5(100 - x^2) = 95$
    \item $7(83 - x^2) = -427$
    \item $-6(2x^2 - 100) = 12$
    \item $3(3-3x^2) = -216$
    \end{enumerate}
    \end{multicols}

\item Solve the following equations for $x$.
    \begin{multicols}{2}
    \begin{enumerate}
    \item $(x^2 + 3) \div 6 = 14$
    \item $(x^2 - 9) \div 10 = 4$
    \item $\displaystyle \frac{x^2 + 39}{4} = {12}$
    \item $\displaystyle \frac{x^2 - 72}{7} = {49}$
    \item $\displaystyle \frac{8 - x^2}{6} = {2}$
    \item $\displaystyle \frac{24 - 2x^2}{12} = {-4}$
    \end{enumerate}
    \end{multicols}

\item Oliver wants to cut a square sheet of paper with an 
area of 25cm$^2$. How long should the sides of the square be?

\item The library wants to build 7 identical square study rooms. 
If the total area of the space will be 63m$^2$, what will be 
the dimensions of the rooms?

\item Zena is planning to fashion a sphere out of some sheet
metal. If the area of sheet metal she can use is 3,217cm$^2$, 
what will be the radius of her sphere? (The surface area ($A$) of 
a sphere is given by its radius ($r$) with the 
formula $A = 4\pi r^2$).

\item Layla wants to expand her square paddock so that each 
side is 3m longer. If the new area of the paddock will be 169m$^2$ 
what was the original area of the paddock?

\item Cooper cuts 12 identical squares out of a sheet of A4 paper. 
The paper has dimensions 297mm by 210mm, if the remaining piece 
of paper has an area of 41,202mm$^2$ what is the side length of
each square?

\item Natalie drops a ball from the top of a 100m tall building. 
The height of her ball above the ground ($h$ meters) after $t$ 
seconds of travel time is modelled by the equation 
$h = 100 - 10t^2$.

\begin{enumerate}
    \item How high will the ball be after 1.5 seconds?
    \item After how many seconds will the ball be 10m above
    the ground.
    \item How many seconds will it take for the ball to hit the 
    ground.
\end{enumerate}

\item Dylan is being launched into space on a rocket. The 
computer modelling predicts that his height above sea level 
($h$ meters), after $t$ seconds, should be modelled 
by the equation $h = 150 + 45t^2$.

\begin{enumerate}
    \item How high above sea level is Dylan before the rocket 
    launches?
    \item How long should it take for Dylan to be 1km above 
    sea level?
    \item The model is wrong, and Dylan is
    only ever one quarter the height that the model predicts.
    How high will he actually be after 7 seconds?
    \item With this new reality in mind, how many seconds will 
    it actually take for Dylan to be 1km above sea level?
\end{enumerate}

\item A new water bottle is a rectangular prism with a square base.
Four of these water bottles are each filled until the water
in each bottle reaches 12cm. The total water poured into the 
bottles is 1,452ml. (Remember that 1cm$^3$ = 1ml)

\begin{enumerate}
\item How long are the sides of the square bases on each 
water bottle?
\item If each water bottle is 20cm tall, how much water would 
all four bottles hold together?
\end{enumerate}

\item Explain why the equation $x^2 + 36 = 0$ has no 
real solutions.

\end{enumerate}

\newpage
\subsection*{Answers}

\begin{enumerate}
\item 
    \begin{multicols}{2}
    \begin{enumerate}
    \item $x = \pm 3$
    \item $x = \pm 1$
    \item $x = \pm 21$
    \item $x = \pm 13$
    \item $x = 0$
    \item $x = \pm 14.14$ ($x = \pm 10 \sqrt{2}$ as an exact value)
    \end{enumerate}
    \end{multicols}

\item
    \begin{multicols}{2}
    \begin{enumerate}
    \item $x = \pm 3$
    \item $x = \pm 7$
    \item $x = \pm 3$
    \item $x = \pm 9$
    \item $x = \pm 8$
    \item $x = \pm 13$
    \item $x = \pm 6$
    \item $x = \pm 9$
    \item $x = \pm 10$
    \item $x = \pm 6$
    \item $x = \pm 13$
    \item $x = \pm 8$
    \end{enumerate}
    \end{multicols}

\item
    \begin{multicols}{2}
    \begin{enumerate}
    \item $x = \pm 3$
    \item $x = \pm 12$
    \item $x = \pm 2$
    \item $x = \pm 7$
    \item $x = \pm 4$
    \item $x = \pm 12$
    \item $x = \pm 9$
    \item $x = \pm 12$
    \end{enumerate}
    \end{multicols}

\item
    \begin{multicols}{2}
    \begin{enumerate}
    \item $x = \pm 5$
    \item $x = \pm 11$
    \item $x = \pm 10$
    \item $x = \pm 6$
    \item $x = \pm 7$
    \item $x = \pm 4$
    \item $x = \pm 6$
    \item $x = \pm 9$
    \item $x = \pm 5$
    \item $x = \pm 3$
    \end{enumerate}
    \end{multicols}

\item
    \begin{multicols}{2}
    \begin{enumerate}
    \item $x = \pm 5$
    \item $x = \pm 4$
    \item $x = \pm 2$
    \item $x = \pm 4$
    \item $x = \pm 9$
    \item $x = \pm 12$
    \item $x = \pm 7$
    \item $x = \pm 5$
    \end{enumerate}
    \end{multicols}

\item
    \begin{multicols}{2}
    \begin{enumerate}
    \item $x = \pm 9$
    \item $x = \pm 7$
    \item $x = \pm 3$
    \item $x = \pm 11$
    \item $x = \pm 4$
    \item $x = \pm 6$
    \end{enumerate}
    \end{multicols}

\item 5cm

\item 3m $\times$ 3m

\item 16.00cm

\item 100m$^2$

\item 42mm

\item
    \begin{enumerate}
    \item 77.5m
    \item 3 seconds
    \item 3.16 seconds or $\sqrt{10}$ in exact form.
    \end{enumerate}

\item
    \begin{enumerate}
    \item 150m
    \item 4.35 seconds
    \item 588.75m
    \item 9.25 seconds
    \end{enumerate}

\item
    \begin{enumerate}
    \item 5.5cm
    \item 2,420ml
    \end{enumerate}

\item If we simplify  the equation we get $x^2 = -36$ and since
the square of any number (positive or negative) is positive, it 
is impossible for the square of a real number to equal $-36$.

\end{enumerate}

\end{document}
